Interim report

### 2018-05-18 DraftReport.tex
future CMIP5 scenarios and density plot on time series

>>>>

\subsubsection{Different future scenarios}
Comparing the different carbon scenarios can also give an idea how sensitive the area is to composition changes in the atmosphere. The rcp26 seems like a unlikely scenario, wheras rcp45 is a possible outcome and rcp85 is the worst imaginable so far, with hopes that big enough changes will be introduced to avoid it. So if we compare the result of these two scenarios, we can see that the two scenarios mostly behave in a similar way, but not everywhere. A first interesting observationin fig \ref{R14585} is that the two graphs do not start in the same place, eventhough that is historical data and not future data. Secondly, rcp45 is decreasing until around 2060 and flatens out after that, wheras rcp85 has a steady decline for the entire period. This is potentially the reson for why that scenario goes down to a lower level, beacuse they are bout around 192 days in 2060. Fig \ref{R104585} instead shows a nearly identical behaviour in both graphs. Once again, they start at different values (1 day difference) but show an increasing and decreasing bahaviour in the same places except the final years where rcp85 shows a big drop in days which is not at all visible in the rcp45 scenario. Fig \ref{R204585} behaves slightly different compared to the other graphs, with rcp45 scenario starting at a larger value then rcp85 and varies more between years. But both graphs has the same ranges, indicating that they differ very little from each other. 
So with a large carbon emisson, we seems to have the largest effect on number of rainy days and least on larger rain amounts. This should mean that it will be more days with small rain amounts. But as seen, the models are not very good at simulating heavy rainfall, which means that there will be a bigger increase in heavy rainfall.
\begin{figure}[H]
	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\linewidth]{R1GCM45mean.pdf}
		\caption{rcp4.5}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\linewidth]{R1GCM85mean.pdf}
		\caption{rcp8.5}
	\end{subfigure}
	\caption{R1mm for rcp 45 and rcp85 scenario 1980-2100}
	\label{R14585}
\end{figure}

\begin{figure}[H]
	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\linewidth]{R10GCM45mean_long.pdf}
		\caption{rcp4.5}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\linewidth]{R10GCM85mean_long.pdf}
		\caption{rcp8.5}
	\end{subfigure}
	\caption{R10mm for rcp 45 and rcp85 scenario 1980-2100}
	\label{R104585}
\end{figure}

\begin{figure}[H]
	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\linewidth]{R20GCM45mean.pdf}
		\caption{rcp4.5}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\linewidth]{R20GCM85mean.pdf}
		\caption{rcp8.5}
	\end{subfigure}
	\caption{R20mm for rcp 45 and rcp85 scenario 1980-2100}
	\label{R204585}
\end{figure}
